|

### 2021-04-26 02-Chp-Systematic-Review-Tools.Rmd
End of day: -2835

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = TRUE}
Why are open source statistical programming  
languages the best?

@@

```{r setup, include=FALSE}
source("R/doc_options.R")
source("R/helper.R")
library(medrxivr)
```

@@

[Need to include bit on linking to published version via the tool]{.correction}

## Main points (to be removed)

The main points I want to get across in this Chapter are:

-   Why searching preprints is important

-   Why existing methods are not sufficient

-   What the `medrxivr` tool adds

@@

Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature. At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[\@bramer2018a;\@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations. As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.

@@

```{r, echo = FALSE}

@@

*Not sure where this should go, but keen to include it*

@@

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = FALSE}
Why are open source statistical programming  
languages the best?

@@

```{r setup, include=FALSE}
source("R/doc_options.R")
source("R/helper.R")
library(medrxivr)
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

@@

Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature. At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018a;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations. As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.

@@

```{r, echo = FALSE, warning=FALSE}

@@

@@

\newpage

## References

### 2021-04-26 05-Chp-CPRD-Analysis.Rmd
End of day: -2835

---
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: default
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = TRUE}
When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
```
(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/Chp2-Systematic-Review.R")
```

@@

Might be able to get around this by pointing out

## Things we tried

- Conditioning entry to the cohort on QRISK score (as defined by codes) rather than. Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly. Need total number of those starting and average time to start.
- Positive controls. Need to be able to explain why these controls have such wildly increased results.
- Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results
- Allowing for time-varying confounders for binary covariates.
- Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.

## Things we could try

@@

## Lay summary

The CPR

@@

@@

### Data source

@@

@@

_Note: If protocol was written by Venexia, how do I reference this?_

@@

### Study Cohort

Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4mmol/L; or an LDL-c test result of >2mmol/L.

@@

@@

@@

The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes. All
covariates were determined at index and definitions for each can be found in Supplementary Table 1.

@@

@@

@@

@@

<!--- Show comparison of code lists here --->

<!----------------------------------------------------------------------------->
``` {r smeeth-comparison-setup, results="hide", message=FALSE}
```

```{r smeeth-comparison-table, message=FALSE, results="asis"}
```
<!----------------------------------------------------------------------------->

@@

@@

Reporting

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = FALSE}
When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
```
(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/Chp3-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?)

__Things we tried__

- Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by . Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly. Need total number of those starting and average time to start.
- Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper.
- Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results
- Allowing for time-varying confounders for binary covariates.

__Things we could try__

@@

<!----------------------------------------------------------------------------->

## Lay summary
Large scale database such as this are often called population level, and studies that make use of them have a number of advantages.

This analysis uses one of these databases, the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of XXXXXX people from YYYYYY general practices across England.

Using this data, I have analysed the ...

<!----------------------------------------------------------------------------->

@@

Large scale databases advantages over other means

Cross reference here aswell re: the lack of information on Vascular dementia and the need for analyses at different sources of bias.

<!----------------------------------------------------------------------------->

@@

### Data source {#cprd-data-source}

@@

The CPRD uses a coding system called Read code <!--- check capitalisation --->

@@

<!-- Note: If protocol was written by Venexia, how do I reference this? -->

@@

### Study cohort

Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.

@@

<!--- Include short bit on follow-up here, describing how and why it was defined --->

@@

A range of additional variables were included in the analysis, intended to address differential distributions of potnetial confounding variables between those who had a

@@

The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010),

Charlson co-morbidity index,

Index of Multiple Deprivation (IMD),

consultation rate,

alcohol (current, former,  never),

smoking (current, former,  never),

BMI,

baseline total cholesterol,

and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.

All covariates were determined at index and definitions for each can be found in Supplementary Table 1.

### Missing data

Missing data was handled using a multiple imputation approach. Variables with missing observations were identified, and

Binary variables were modelled using a

continuo

As per best practice, all other variables, including the out

The MICE command in Stata was used

### Time axis

In Cox models, there is the option to

Age vs time-since entry

@@

### Immortal time bias and time-varying treatment indicators

Immortal time bias is a type of misclassification bias. It occurs when

One potential way to address this is the use of a time-varying treatment indicator, a factor which modi

In the case of this analysis, this treatment indicator is statin use. Using codes for statins (see Appendix \@ref())

<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->

@@

<!--- This hasn't been done! --->

@@

However, there was a large difference in the case mix of dementia diagnoses between the two analyses.

However, as shown in Table \@ref(tab:smeethComparison-table), there is substantial divergence between the two sets of code-lists.

The reason for the discrepancy in terms of the number of Alzheimer cases as a percentage of total dementia cases between our study and the Smeeth 2010 paper is due to two things:
•	While all of the codes used to define Alzheimer’s in the Smeeth paper are included in our “Probable Alzheimer’s” code-list, we also have several additional codes used to define this outcome (including, for example, “Eu00013: [X]Alzheimer's disease type 2”). 
•	Several of the codes in our “Possible Alzheimer’s” code list are included in the “Other dementia” code list used by Smeeth.

Using the Smeeth code-list, we get a similar breakdown of cases to that paper, with Alzheimer’s disease being a lot less frequent than when using our code-lists (which is not surprising based on the points above). <!-- This, in addition to unexplained statistical issues such as adjusting for post-baseline covariates, means I am sceptical of the value of comparing our findings with Smeeth. -->

Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.

<!----------------------------------------------------------------------------->
(ref:smeethComparison-caption) Comparison of code lists used in this analysis and in Smeeth et al.

(ref:smeethComparison-scaption) Comparison of code lists used in this analysis and in Smeeth et al.

```{r smeethComparison-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

@@

A further limitation is the possibility of time-varying confounding <!--- Either deal with this issue here, or keep the section above dealing with time-varying confounding. --->

@@

Reporting guidelines do not always work, but help to guide

All code and summary statistics (i.e. the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats, without any formatting, from the Github repository for this project.
